\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work, we find significant differences in predictive performance across
different splitting schemes.

The most common scheme for drug--target interaction prediction is the
split over drug-target pairs \cite{Survey2018} where it may happen
that most drugs and targets that are including in the model's
validation and testing phase have also been included in the training
phase (as part of other drug--target pairs).

@@

@@

\todo[inline]{Likely discussion:}
Assuming a hypothetical, perfectly generalizing model built upon an
unbiased dataset, this very model would yield similar performances for
all three , not overfitting on the known
structures. On the other hand, for a hypothetical entirely overfitting
model, trained on a highly biased dataset, this model would show
substantial deviations from the original performance over another
split.

\todo[inline]{Likely discussion:}
We emphasize, that all real-world models are prone to some sort of
overfitting, and unknown, deviant entities in both validation and
testing set will likely lead to some sort of performance gap for
relevant metrics. However, a large disparity may hint the biases
stated above.

@@

>>>>

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{}, we find significant differences in predictive
performance across different splitting schemes.

The most common scheme for drug--target interaction prediction is the
split over drug-target pairs \cite{Survey2018} where it may happen
that most drugs and targets that are including in the model's
validation and testing phase have also been included in the training
phase (as part of other drug--target pairs). This scheme is prone to a
number of biases. If the number of interactions for a drug or protein
are imbalanced, i.e., some drugs or proteins have many more
interactions than others, these will be seen more often during
training and they will likely also have more interactions in the
testing and validation sets. Preferentially predicting

@@

Other biases: evaluate on balanced data, not all

@@

@@

% \todo[inline]{Likely discussion:}
% Assuming a hypothetical, perfectly generalizing model built upon an
% unbiased dataset, this very model would yield similar performances for
% all three , not overfitting on the known
% structures. On the other hand, for a hypothetical entirely overfitting
% model, trained on a highly biased dataset, this model would show
% substantial deviations from the original performance over another
% split.

% \todo[inline]{Likely discussion:}
% We emphasize, that all real-world models are prone to some sort of
% overfitting, and unknown, deviant entities in both validation and
% testing set will likely lead to some sort of performance gap for
% relevant metrics. However, a large disparity may hint the biases
% stated above.
